\toolname: file-based localization of numerical perturbations in data analysis pipelines

### 2020-04-22 paper.tex

\toolname identifies the components in a pipeline, at the resolution level of a system process, that produce different
results in different execution conditions. First, a directed
bipartite provenance graph is recorded for each pipeline execution, where nodes
represent application processes and files, and edges represent read and
write file accesses (Figure~\ref{fig:provenance-graph}). Second,
transient files, i.e., files that are either deleted during pipeline
execution or modified by multiple processes, are identified and
disambiguated, resulting in a provenance DAG (Directed Acyclic
Graph) in which file nodes have a single parent (in-degree of 1) (Figure~\ref{fig:provenance-dag}). 
DAGs produced in different conditions are then compared, in
a step-by-step execution that prevents the propagation of differences in the pipeline (Figure~\ref{fig:labeled-dag}).
 The resulting labeled graph identifies the
non-reproducible processes in the pipeline. 
\note{The graphs show all executed processes captured by the \reprozip tool
except those that their binaries are placed in directory \texttt{/usr/bin/}. 
We excluded these processes for a better representation of the pipeline execution.}

@@

\begin{minipage}{\linewidth}
  \centering
    \includegraphics[width=\linewidth]{figures/pfs-labeled.pdf} 
    \caption{A complete provenance graph from the PreFreesurfer pipeline.}
    \label{fig:complete_pfs}
\end{minipage}
\end{figure*}

>>>>

\toolname identifies the components in a pipeline, at the resolution level of a system process, that produce different
results in different execution conditions. First, a directed
bipartite provenance graph is recorded for each pipeline execution, where nodes
represent application processes and files, and edges represent read and
write file accesses (Figure~\ref{fig:provenance-graph}). Second,
transient files, i.e., files that are either deleted during pipeline
execution or modified by multiple processes, are identified and
disambiguated, resulting in a provenance DAG (Directed Acyclic
Graph) in which file nodes have a single parent (in-degree of 1) (Figure~\ref{fig:provenance-dag}). 
DAGs produced in different conditions are then compared, in
a step-by-step execution that prevents the propagation of differences in the pipeline (Figure~\ref{fig:labeled-dag}).
 The resulting labeled graph identifies the
non-reproducible processes in the pipeline. 
\note{Ali}{The graphs show all executed processes captured by the \reprozip tool
except those that their binaries are placed in directory \texttt{/usr/bin/}. 
We excluded these processes for a better representation of the pipeline execution.}

@@

\begin{minipage}{\linewidth}
  \centering
    \includegraphics[width=\linewidth]{figures/pfs-labeled.pdf} 
    \caption{A complete provenance graph from the PreFreesurfer pipeline.
    \note{Ali}Full-resolution image is available \href{https://github.com/big-data-lab-team/HCP-reproducibility-paper/blob/master/figures/pfs-labeled-orig.pdf}{here}.}
    \label{fig:complete_pfs}
\end{minipage}
\end{figure*}
